Convective heat transport in stratified atmospheres at low and high Mach number

### 2017-06-20 tex/nusselt_paper.tex
fixes flywheel discussion

We measure the adiabatic Mach number (Ma = $|\bm{u}|/\sqrt{\gamma T}$),
and find that it is a strong function of 
$\epsilon$ and a weak function of Ra.  
In our 2D runs, when Ma $< 1$, we observe a scaling law of
Ma(Ra$, \epsilon) \appropto \epsilon^{1/2}$Ra$^{1/4}$.
This relation breaks down as the mean
Ma approaches 1 (see Fig. \ref{fig:ma_v_eps}).  This transition
occurs near Ra/Ra$_\text{crit} \approx \{10^{2}, 10^{3}\}$ for $\epsilon = \{1, 0.5\}$.
We conjecture that the scaling of Ma with Ra is due to high-velocity ``spinners'' which
form between upflow and downflow lanes in 2D, and which are constantly fed by 
the relatively stationary upflows and downflows (BEN NEED CITES).
In our limited 3D runs, Ma appears to be a function of $\epsilon$ alone, with
Ma $\appropto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
Simulations in the range of Ra/Ra$_{\text{crit}} > 10^3$ at $\epsilon = 10^{-4}$
exhibited ``windy'' states of convection, in which a large-scale horizontal
shearing flow replaced the more standard upflow/downflow morphology of
convection, similar to analogous states which have been studied in
RB convection \cite{goluskin&all2014}.  These states are represented in Figs. 
\ref{fig:ma_v_eps}, \ref{fig:re_and_nu_v_ra}, \& \ref{fig:nrho_v_ra}
as hatched points, and while this phenomeonon does not appear to greatly modify the
scaling of fluid properties measured in this work, these states warrant
further investigation.

>>>>

We measure the adiabatic Mach number (Ma = $|\bm{u}|/\sqrt{\gamma T}$),
and find that it is a strong function of 
$\epsilon$ and a weak function of Ra.  
In our 2D runs, when Ma $< 1$, we observe a scaling law of
Ma(Ra$, \epsilon) \appropto \epsilon^{1/2}$Ra$^{1/4}$.
This relation breaks down as the mean
Ma approaches 1 (Fig. \ref{fig:ma_v_eps}).  This transition
occurs near Ra/Ra$_\text{crit} \approx \{10^{2}, 10^{3}\}$ for $\epsilon = \{1, 0.5\}$.
In our limited 3D runs, Ma appears to be a function of $\epsilon$ alone, with
Ma $\appropto \epsilon^{1/2}$, so at high Ra, Ma$_{\text{3D}} < \text{Ma}_{\text{2D}}$.
We conjecture that the scaling of Ma with Ra in the 2D runs 
is due to the formation of coherent high-velocity ``spinners,'' which form
between upflow and downflow lanes in 2D.  These structures, which are reminiscent of flywheel
modes in RB convection, do not appear in our 3D runs these parameters
\cite{jones&all1976, brummell&all2002}.
Simulations in the range of Ra/Ra$_{\text{crit}} > 10^3$ at $\epsilon = 10^{-4}$
exhibited ``windy'' states of convection, in which a large-scale horizontal
shearing flow replaced the more standard upflow/downflow morphology of
convection, similar to analogous states which have been studied in
RB convection \cite{goluskin&all2014}.  These states are represented in Figs. 
\ref{fig:ma_v_eps}, \ref{fig:re_and_nu_v_ra}, \& \ref{fig:nrho_v_ra}
as hatched points, and while this phenomeonon does not appear to greatly modify the
scaling of fluid properties measured in this work, these states warrant
further investigation.
